Manuscript_draft

### 2021-01-01 manuscript_draft.Rmd
more manny changes

@@

>>>>

```{r periodic increment by treatment level}

# Create a function to compute standard error for vectors with NA
incSE<-function(x) {

  x2<-
    x %>% 
    .[!is.na(.)]

    sd(x2)/sqrt(length(x2)) %>% 
    return()
  }

perInc.X<-
  plotData.X %>% 
  pivot_longer(cols=Vol.sum:QMD.mean,names_to="var",values_to = "val") %>% 
  pivot_wider(names_from = Year,values_from = val) %>% 
  mutate(Period1=(`1994`-`1992`)/3,
         Period2=(`1997`-`1994`)/3,
         Period3=(`2009`-`1997`)/11,
         Period4=(`2019`-`2009`)/11) %>% 
  dplyr::select(BA.Target:var,Period1:Period4) %>% 
  pivot_longer(cols=Period1:Period4,names_to="Period",values_to="Values") %>% 
  pivot_wider(names_from=var,values_from=Values) %>%

  # now summarize at treatment unit level
  group_by(BA.Target,Period) %>% 
   summarise(Vol=mean(Vol.sum,na.rm=T),
            Vol.se=incSE(Vol.sum),
            BA=mean(BA.sum,na.rm=T),
            BA.se=incSE(BA.sum),
            SPH=mean(SPH.sum,na.rm=T),
            SPH.se=incSE(SPH.sum),
            QMD=mean(QMD.mean,na.rm=T),
            QMD.se=incSE(QMD.mean))

# create captions for figures and table
figNums("perInc.plot",display=FALSE)
appNums("perInc.table",display=FALSE)

@@

```{r plot periodic increment}

periodInc.plot<-function(standVar,y.label){

  perInc.X %>%
  dplyr::select(BA.Target,Period,standVar,paste0(standVar,".se")) %>% 
    setNames(c("BA.Target","Period","Mean","SE")) %>%

  ggplot(aes(x=Period,y=Mean,group=BA.Target,color=BA.Target))+
  geom_point()+
  geom_line()+
     geom_errorbar(aes(ymin=Mean-SE, ymax=Mean+SE, width=.2),
                   position=position_dodge(0)) %>% 
    return()
}

periodInc.plot("BA",y.label="BA (m²/ha)")
periodInc.plot("Vol",y.label="BA (m²/ha)")
